An Improved Method for Coupling Hydrodynamics with Astrophysical Reaction Networks

### 2022-07-21 simplified_sdc_intro/paper.tex
add new plot

Figure \ref{fig:subch_strang_cfl02} shows the temperature, mean
molecular weight, and nuclear energy generation rate for the Strang splitting
CFL = 0.2 simulation ({\tt strang\_subch2\_cfl0.2}).  At this point
in the evolution, the helium detonation has wrapped more than halfway
across the surface and the ingoing carbon detonation is approaching the
center of the star.  We see that the
mean molecular weight appears mottled behind the inward propagating
detonation in the white dwarf.  Comparing to the energy generation
rate, we see that region is characterized by large energy releases of
alternating signs checkerboarding thoughout the region.  This is
characteristic of the nucleosynthesis struggling to come into
equilibrium at high temperatures when the reverse rates can be
important.

@@

>>>>

Figure \ref{fig:subch_strang_cfl02} shows the temperature, mean
molecular weight, and nuclear energy generation rate for the Strang splitting
CFL = 0.2 simulation ({\tt strang\_subch2\_cfl0.2}).  At this point
in the evolution, the helium detonation has wrapped more than halfway
across the surface and the ingoing carbon detonation is approaching the
center of the star.  We see that the
mean molecular weight appears mottled behind the inward propagating
detonation in the white dwarf.  Comparing to the energy generation
rate, we see that region is characterized by large energy releases of
alternating signs checkerboarding thoughout the region.  This is
characteristic of the nucleosynthesis struggling to come into
equilibrium at high temperatures when the reverse rates can be
important.  \added{To highlight this, Figure~\ref{fig:strang_steps} shows the nuclear
energy generation rate in a highly-zoomed region around the detonation over four
consecutive coarse timesteps.  We see that on the detonation front itself, the
sign of the energy generation rate changes from one step to the next in many zones.}

@@

\begin{figure}
\centering
\plotone{strang_step_diff_summary_plot}
\caption{\label{fig:strang_steps} Energy generation rate for the
  Strang CFL = 0.2 run with normal tolerances ({\tt
    strang\_subch2\_cfl0.2}) shown at 4 consecutive timesteps around
  $t = 0.1~\mathrm{s}$ zoomed in at the inward propagating detonation.}
\end{figure}
